Network Configuration Synthesis with Abstract Topologies

### 2016-11-11 paper/abstraction/paper.tex
update examples for consistency

\begin{figure}[t]\small
  \begin{minipage}[t]{\linewidth}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{rclr}
     pol     &::=& p_1, \dots, p_n & \textit{policies} \\
     p       &::=& t \hspace{.3em} \Path \hspace{.3em} r_1 \Prefer \dots \Prefer r_m & \textit{constraints} \\
     t       &::=& \$x \BNFALT d.d.d.d/[d..d] \hspace{1.5em} & \textit{template variable} \\
     r       &::=& l & \textit{location} \\
         &\BNFALT& \emptyset & \textit{empty set} \\
         &\BNFALT& \In & \textit{internal loc} \\
         &\BNFALT& \Out & \textit{external loc} \\
         &\BNFALT& r_1 \cup r_2 & \textit{union} \\
         &\BNFALT& r_1 \cap r_2 & \textit{intersection} \\
         &\BNFALT& r_1 \cdot r_2 & \textit{concatenation} \\
         &\BNFALT& \NOT r & \textit{path negation} \\
         &\BNFALT& r^* & \textit{iteration} \\
  \end{array} \]%

  \end{minipage}
  \vspace{1em}
  \caption{Simplified \sysname syntax.}
  \label{fig:syntax}
  %\vspace{-1em}
\end{figure}%

>>>>

\begin{figure}[t]\small
  \begin{minipage}[t]{\linewidth}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{rclr}
     pol     &::=& p_1, \dots, p_n & \textit{policy} \\
     p       &::=& t \hspace{.3em} \Path \hspace{.3em} r_1 \Prefer \dots \Prefer r_m & \textit{path preferences} \\
     t       &::=& \$x \BNFALT d.d.d.d/[d..d] \hspace{1.5em} & \textit{predicate} \\
     r       &::=& l \BNFALT \emptyset \BNFALT \In \BNFALT \Out \BNFALT r_1 \cup r_2 \BNFALT & \textit{regular path} \\
             &   & r_1 \cap r_2 \BNFALT r_1 \cdot r_2 \BNFALT \NOT r \BNFALT r^* \\
%         &\BNFALT& \emptyset & \textit{empty set} \\
%         &\BNFALT& \In & \textit{internal loc} \\
%         &\BNFALT& \Out & \textit{external loc} \\
%         &\BNFALT& r_1 \cup r_2 & \textit{union} \\
%         &\BNFALT& r_1 \cap r_2 & \textit{intersection} \\
%         &\BNFALT& r_1 \cdot r_2 & \textit{concatenation} \\
%         &\BNFALT& \NOT r & \textit{path negation} \\
%         &\BNFALT& r^* & \textit{iteration} \\
  \end{array} \]%

  \end{minipage}
  \vspace{-.3em}
  \caption{Simplified \sysname syntax.}
  \label{fig:syntax}
  %\vspace{-1em}
\end{figure}%
